Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code

### 2015-06-10 fib2.tex
a couple more comments
minor

We consider a 
2-dimensional system with
point-like excitations or quasiparticles known as anyons.
These anyons show exotic statistics under exchange.
The worldlines of these exchanges form \emph{braids}
in (2+1)-dimensions
which act unitarily on (the Hilbert space of) degrees of freedom known as the \emph{fusion space.}
To access this space we define
the topological observables of the system: these
are total charge measurements within regions bounded by \dude{directed} closed loops (Wilson loops).
%The algebraic properties of these processes
These dynamics and observables obey algebraic rules
given by a unitary modular tensor category~\cite{Wang2010b}. % (UMTC). 
However, from the perspective of
\emph{topological quantum field theory}
anyons are modelled
as punctures in a surface~\cite{Pfeifer2014}, and it is not
the anyons themselves that braid,
but the manifold in which the anyons reside 
that becomes deformed (twisted) by these braid moves.
This is the perspective we adopt (see \Fref{f:braidloop}).
\dude{Fig or FIG ?}
%In particular, this shows the action of braiding
%on arbitrary observables (Wilson loops) as
%these deform with the manifold.

@@

%The state \dude{space?} of a collection of anyons
%can be described by the observables of the system.
The \dude{key?} difference between abelian and non-abelian
anyon theories is that the outcomes of measurements in an abelian theory
are determined uniquely particle content only.
%The defining characteristic of a \emph{non-abelian}
%anyon theory is that ...
That is, the fusion space is one-dimensional for abelian anyons, and generally larger for non-abelian anyons.
In particular, we consider a system supporting (non-abelian) Fibonacci
anyon excitations, denoted by $\tau.$
Two such anyons can have total charge
that is a superposition of $\tau$ and $\vac$ (vacuum),
so the fusion space in this case is 2-dimensional.
We can represent basis states for this space using diagrams 
of definite total charge for the Wilson loops, 
and arbitrary states as linear combinations of these diagrams:
\begin{align*}
\includegraphics[]{pic-fibonacci.pdf}
\end{align*}
For $n$ anyons of type $\tau$, the 
dimension of this space grows asymptotically as $\varphi^n$ for $\varphi=\frac{1+\sqrt{5}}{2}$ 
the golden ratio.

>>>>

We consider a 
2-dimensional system with
point-like excitations or quasiparticles known as anyons.
These anyons show exotic statistics under exchange.
The worldlines of these exchanges form \emph{braids}
in (2+1)-dimensions
which act unitarily on (the Hilbert space of) degrees of freedom known as the \emph{fusion space.}
To access this space we define
the topological observables of the system: these
are total charge measurements within regions bounded by \dude{directed} closed loops (Wilson loops).
%The algebraic properties of these processes
These dynamics and observables obey algebraic rules
given by a unitary modular tensor category~\cite{Wang2010b}. % (UMTC). 
However, from the perspective of
\emph{topological quantum field theory}
anyons are modelled
as punctures in a surface~\cite{Pfeifer2014}, and it is not
the anyons themselves that braid,
but the manifold in which the anyons reside 
that becomes deformed (twisted) by these braid moves.
This is the perspective we adopt (see \Fref{f:braidloop}).
%\dude{Fig or FIG ?} -- it's Fig.
%In particular, this shows the action of braiding
%on arbitrary observables (Wilson loops) as
%these deform with the manifold.

@@

%The state \dude{space?} of a collection of anyons
%can be described by the observables of the system.
The \dude{key?} difference between abelian and non-abelian
anyon theories is that the outcomes of measurements in an abelian theory
are determined uniquely by particle content only.
%The defining characteristic of a \emph{non-abelian}
%anyon theory is that ...
That is, the fusion space is one-dimensional for abelian anyons, and generally larger for non-abelian anyons.
In particular, we consider a system supporting (non-abelian) Fibonacci
anyon excitations, denoted by $\tau.$
Two such anyons can have total charge
that is a superposition of $\tau$ and $\vac$ (vacuum),
so the fusion space in this case is 2-dimensional.
We can represent basis states for this space using diagrams 
of definite total charge for the Wilson loops, 
and arbitrary states as linear combinations of these diagrams:
\begin{align*}
\includegraphics[]{pic-fibonacci.pdf}
\end{align*}
For $n$ anyons of type $\tau$, the 
dimension of this space grows asymptotically as $\varphi^n$ for $\varphi=\frac{1+\sqrt{5}}{2}$ 
the golden ratio.
